Draft

### 2019-12-11 Group1Prez.Rmd

- Paper discussed calculating the probability that one player, A, wins a tennis match against another player, B

- Based on other papers involving calculating the probability of winning a game in other racket sports the conclusion was made to treat points in tennis as  independent identically distributed (iid) random variables

- Although it is noted at points in tennis are not iid for most purposes this is not a bad assumption as the divergence from iid is small

  - This was supported by a statistical anaylsis of 4 years of Wimbledon data

>>>>

- Paper discussed how the probability of winning a game, a set, and a match in tennis are computed based on each player's probability of winning a point on a serve

- Based on other papers the conclusion was made to treat serves in tennis as independent identically distributed (iid) random variables

- It is noted that points in tennis are not iid for most purposes this is not a bad assumption as the divergence from iid is small

- Both two out of three and three out of five set matches were considered aloowing for 13-point tiebreaker in each set if needed

### 2019-12-11 PaperDraft.Rmd
Outline
echo = FALSE

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Motivation

- Explination of Game, Set, Match

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### Motivation 
The probability of winning a game, a set, and a match in tennis are calculated based on the each's players probability of winning a point on a serve. This paper and the reference paper, The Probability of Winning at Tennis 1. Theory and Data written by Paul K. Newton and Joseph B. keller both make the assumption that each serve is an independently and identically distributed (iid) random variable. This assumption has been made in other reports relating to the probability of winning a game in other racuet sports and even though serves in tennis are not actually iid random varibales for most purposes this is not a bad assumption as the divergence from iid is small. 
- Explination of Game, Set, Match

- How likely are the players to win the torunament?

@@

- Reproduce data in paper

@@

- Same thing with new tournament

- Maybe with new method if we have time

### Bibliography
